---
title: "CRIC: (`r parms$anl_name`)"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
bibliography: references.bib
link-citations: true
# csl: nature.csl                        # Citation Style Language file
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="#>")
```

# Project info 

```{r setup, include=FALSE}
# Define variables used in the title
anl_name = parms$anl_name
link_prj_Info = paste0("../../prj_Info.inc")
link_add_vars = paste0("../../cric_add_variables.inc")
link_complete_data = paste0("../../02-cric-df_complete.R")
link_tvars_mtx = paste0("../../cric_tvars_mtx.inc")
link_tvars_mtx1 = paste0("../cric_tvars_mtx.inc")

```

Project related internal links

* [prj_Info.inc](`r link_prj_Info`)
* [02-cric-df_complete.R](`r link_complete_data`)
* [cric_add_variables.inc](`r link_add_vars`)  script used to derive new/modify existing variables in df_complete data
* [cric_tvars_mtx.inc](`r link_tvars_mtx`)

Project info:

```{r prj_info}   #, results='markup'}
prj_Path    = ".."
fpath = paste0(prj_Path, "/prj_Info.inc") 
source(fpath)
prj_Info

```

* Original data name: `r prj_Info$original_nms["df"]` stored in `r  paste0("./data/", prj_Info$original_nms["Rdata"])`
* Data frame `df_complete` stored in `r prj_Info$complete_nms["Rdata"]`
* `d_cols` vector
```{r d_cols-vector}
tmp = prj_Info$d_cols
tmp1 = c(names(tmp))
dx = rbind(tmp1,tmp)
rownames(dx) = NULL
```

# Data

## Original data

Glimpse of original data

```{r original_data, results='markup'}
Rdata_path = paste0("../data/", prj_Info$original_nms["Rdata"])
df_load = load(Rdata_path)
df_orig  =  get(df_load)
glimpse(df_orig)
```

### Missing values

Report on missing values

```{r df_orig_miss}
generate_missing_value_report <- function(data, ...) {

  missing_summary <- data %>%
    summarise_all(~ sum(is.na(.))) %>%
    pivot_longer(cols = everything(), names_to = "Column", values_to = "MissingCount") %>%
      filter(MissingCount != 0)
  
  cat("\nSummary of Missing Values by Column:")
  print(missing_summary, n=99)
  
  # Generate skim summary
  skimmed_data = skim(data, ...)
  return(skimmed_data)
}

# Generate the report
skimmed_data = generate_missing_value_report(df_orig, .data_name = "df_orig")
knit_print(skimmed_data)  

```

Missing values plot


```{r missing_plot, fig.width=6, fig.height=4, fig.align='center', fig.cap='Missing values Plot', out.width='80%'}
# Example plot
generate_missing_value_plot <- function(data) {
  missing_plot <- data %>%
    summarise_all(~ sum(is.na(.)) / n()) %>%
    pivot_longer(cols = everything(), names_to = "Column", values_to = "MissingPercent") %>%
      filter(MissingPercent !=0)
  
  print(ggplot(missing_plot, aes(x = Column, y = MissingPercent)) +
          geom_bar(stat = "identity", fill = "steelblue") +
          coord_flip() +
          labs(title = "Missing Values by Column", x = "Column", y = "Percentage of Missing Values") +
          theme_minimal())
  }
generate_missing_value_plot(df_orig)
```


## Complete data

Link to [code](`r link_complete_data`) used to derive df_complete data


Glimpse of complete dataset (after imputing missing values)

```{r complete_data_glimpse, results='markup'}
Rdata_path = paste0("../data/", prj_Info$complete_nms["Rdata"])
obj_load = load(Rdata_path)
df_complete  =  get(df_load)
glimpse(df_complete)
```

## Derived data

Link to [code](`r link_add_vars`) used to derive new/modify existing variables in df_complete data


# Results

Time vars presented in this website:


```{r tvars_mtx}

source(link_tvars_mtx1) #  tvars_mtx
selx = pmatch(tvar_ids_vec,tvars_mtx[, "id"])
tvars_selx =tvars_mtx[selx,]
tvars_selx
```

```{r Info-list, results='markup'}
anl_Path = paste0(prj_Path,"/Analysis_Info/",anl_name)
fpath = paste0(anl_Path,".inc")
source(fpath)
Info
```

# Citations

* See [@mclernon2023assessing]   at [URL](https://www.acpjournals.org/doi/pdf/10.7326/m22-0844?casa_token=cZTw6iuKYWAAAAAA:lo2v5N4EeqD_0O-h5j3RtaZuHYYBDJc5nOMt79l2lrE8HK3mjKjcyKl_XUJdQiUPMI2VKA4KB5tZlg)
* See [@mlr3]
* See [@sanderson2013derivation] at [URL](https://link.springer.com/content/pdf/10.1186/1471-2288-13-113.pdf)
* See [@van2022validation] at [URL](https://www.bmj.com/content/bmj/377/bmj-2021-069249.full.pdf?casa_token=bzl02Sjp8kYAAAAA:3Xi72CFbReAhAKtCP_7-MfnD8ucX3v78v1LVIS7gG7mEzkwkJjuTmLX7RS1OjI-AH6QDy8TqrII)

# References {-}


