---
title: "CRIC: (`r parms$anl_name`:`r parms$t_varsid`)"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="#>")
```


```{r setup, include=FALSE}
# Define the variables used in the title
anl_name = parms$anl_name
t_varsid = parms$t_varsid
prj_Path    = ".."
anl_Path = paste0(prj_Path,"/", anl_name)

# source tvars_mtx
fpath = paste0(prj_Path, "/cric_tvars_mtx.inc")
source(fpath)

# src Info

fpath = paste0(anl_Path,"/_Infoxvars.inc")
source(fpath)
#tvar_name = Info$target_cols["time"]
selct = tvars_mtx[tvars_mtx[, "id"] == t_varsid, ]
tvar_name  = selct["time"]
event_num  = selct["event.num"]
event_fac  = selct["event.fac"]
tvnpath    =  paste0(anl_Path,"/",t_varsid,tvar_name)
RdataPath =paste0(tvnpath, "_cva_glmnet.Rdata")
xlsxfPath = paste0(tvnpath,"_summary.xlsx")
variaPath = paste0(tvnpath, "_varia.Rdata")
# dim(data1e)


```
# Intro

Results for time variable:

```{r target_cols}
cat(t_varsid, ":", tvar_name, event_num, event_fac)
```

# Input 

## `r anl_name` info


* glmnet_args

```{r glmnet_args, results='markup'}
glmnet_args
```
* ctree_args

```{r ctree_args, results='markup'}
ctree_args
```
* cv_coxboost_args

```{r cv_coxboost_args, results='markup'}
cv_coxboost_args
```
* Info

```{r Info, results='markup'}
Info
```

# Data

```{r data1e_nms}
RdataRes = load(RdataPath)
ResOption1 = if ("surv.cva_glmnet_learners" %in% RdataRes) TRUE else FALSE
names(data1e)
```

Table for `train_ind` variable
  
```{r table_train_ind}
table(train_ind = data1e$train_ind)
```


# Results

Results are stored in

 * .xlsx (`r xlsxfPath`)
 * _cva_glmnet.Rdata (`r RdataPath`)
 * _varia.Rdata (`r variaPath`)

Worksheet names in .xlsx file:


```{r wbSheetNames}
 wb = loadWorkbook(xlsxfPath)
 getSheetNames(xlsxfPath)
```

Objects stored in _cva_glmnet.Rdata file

```{r RdataObjectNames}
RdataRes
```



Glance results: 


```{r  glanceAll}
  ## fpath1 =paste0(anl_Path, "/_prj_info.xlsx")
  glanceAll = readWorkbook(wb, "glanceAll")
  glancex = glanceAll %>%  mutate(across(where(is.numeric),~ round(.x, digits=3))) 
  glancex
```

tidyAll

```{r  tidyAll}

  tidyAll = readWorkbook(wb, "tidyAll")
  tidyx = tidyAll %>%  mutate(across(where(is.numeric),~ round(.x, digits=3))) 
  tidyx
```

Beta coefficients for diffrent values of alpha hyperparameter:


```{r  coefAll}
  ## fpath1 =paste0(anl_Path, "/_prj_info.xlsx")
  coefAll = readWorkbook(wb, "coefAll")
  coefx = coefAll %>%  mutate(across(where(is.numeric),~ round(.x, digits=3))) 
  coefx
```

# LASSO 

## CV-Plot

```{r cv.fit-lasso, include=ResOption1, fig.cap = "Fig: Cross-validation plot"}
cva1_learner= surv.cva_glmnet_learners[["a.1"]]
cva1_fit =cva1_learner$model$model
plot(cva1_fit)
```

## Prediction

Prediction on test data

```{r predict-lasso, include=ResOption1}
cva1_prediction= surv.cva_glmnet_prediction[["a.1"]]
#cva1_fit =cva1_prediction1$model$model
#plot(cva1_fit)
```

# Log

```{r log-execution,results="asis" }
nms = load(file = variaPath)
writeLines(logx)
```







# Conclusion

::: {#box1 .green-box}
Wrapping it up!
:::



# References {-}
